As reward from House Lannister for killing Robb Stark, House Frey receives the Seat of Riverrun, and Roose Bolton is appointed the new Warden of the North.
 Arya and the Hound witness Frey soldiers mocking the desecrated remains of Robb Stark.
 Arya stabs to death one of the men, marking the first time she kills a man, while the Hound kills the others.
 Yara Greyjoy begins a new military campaign to recapture Theon, who has been penectomized at Dreadfort by Lord Bolton's bastard son Ramsay Snow and begs for death in light of Snow's continued torture.
 Tywin chastises Tyrion for not having impregnated Sansa, and for placing his own desires over the needs of family.
 Jaime arrives in the capital with Brienne, and is reunited with Cersei.
 In the North, after crossing paths with Bran and guiding him beyond the Wall, Sam arrives back at Castle Black, where he and Maester Aemon send out ravens to alert the whole of Westeros about the arrival of the White Walkers.
 Ygritte catches up to Jon and tearfully shoots him full of arrows.
 Jon manages to escape and collapses before the gates of Castle Black, where Sam orders him to be cared for.
 At Dragonstone, Davos helps Gendry to escape, and Stannis receives the distress call from the Night's Watch.
 After word from both Melisandre and Davos, he now plans to move north and aid the Watch against the invading darkness.
 And across the Narrow Sea, the freed slaves of Yunkai receive Daenerys as their "mhysa", meaning "mother" in Ghiscari.
